### 2018-05-28 Paper/jaccardbaetica.tex
new changes intro

The analysis shows that amphoric stamps could not be correlated with spatial distance.

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. \ref{dendro} was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.

@@

On the one hand, the use of these amphoric stamps could have been exclusively running by the owner of families to distinguisth the amphora workshop (CITAR). The kind of distintion does not seem to be used to specify the quality or value of the product \citep{callender}. 
On the other hand, it can be interpreted somehow a batch systematic organization (CITAR). Considering that Dressel 20 was not marked in several cases (CITAR), some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped. This method would be used as an identifier to count the number of amphorae of a banch (CITAR). This is would be explain why we found different stamps in a same workshops.

An any case, no podemos precisar a qué se tratase

>>>>

The analysis shows that amphoric stamps could be correlated with the spatial distance. The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. \ref{dendro} was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their production system. No groups of similar stamps were found in the cluster. On the other hand, closer workshops show a similarity on the stamps while most of them seem to display different stamps roles. Indeed workshops that shared more similar amphoric stamps belonged to the same \textit{conventus} area, as for instance Picachos, Cerro de los Pesebres and El Castillejo.

@@

On the one hand, the use of these amphoric stamps could have been exclusively running by the owner of the workshop to distinguish the amphora workshop (CITAR). The kind of distinction does not seem to be used to specify the quality or value of the product \citep{callender}. 
On the other hand, it can be interpreted somehow a batch systematic organization (CITAR). Considering that Dressel 20 was not marked in several cases (CITAR), some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped. This method would be used as an identifier to count the number of amphorae of a branch (CITAR). This it could be explain wherefore we found different stamps in a same workshop.

In any case, no podemos precisar a qué se tratase
